A secondary screen architecture to accurately capture viewers' interactions and contextual information in TV environments

### 2014-05-05 src/paper.tex
Updated abstract

\title{A secondary screen architecture to accurately capture TV viewers' interactions and contextual information in TV environments}

@@

\begin{abstract}
TV watching is frequently seen as a social activity. People gather around the television for entertainment or information. Advances in TV technology have enabled the viewer to actively interact with applications and providers instead of just passively watch TV. One important application for the viewers is content personalization, which consists in generating content recommendations based on viewers' interactions. Since the TV set is shared by many people, it is difficult to accurately capture the individual interactions from every viewer using a traditional remote control. In this paper, we present an architecture that facilitates the identification of viewers and the capture of their individual interactions in shared TV environments.
\end{abstract}

>>>>

\title{A secondary screen architecture to accurately capture viewers' interactions and contextual information in TV environments}

@@

\begin{abstract}
TV watching is frequently seen as a social activity. People gather around the television for entertainment or information. Advances in TV technology have enabled the viewer to actively interact with the TV through interactive applications instead of just passively watch TV. Since the TV set is shared by many people and the interaction occur by using a single remote control, it is difficult to accurately capture the individual interactions from every viewer. It is also difficult to identify the context in which the interactions occur, e.g., the people that are present in the environment. In this paper, we present an architecture that facilitates viewers' individual interactions and contextual information in shared TV environments. One important application of this data consists in generating personalized content for single viewers and groups of viewers.
\end{abstract}
